Final Project Draft #2

### 2022-04-26 draft2.Rmd
Cat Graph

Hours Worked vs. Happiness (factor in city)
Is there a correlation between happiness and hours worked?
#This one is still a work in progress
```{r}
##waiting on revised hours worked data
healthy_data_dollars %>% 
  select(`City`, "Happiness Level" = `Happiness levels(Country)`, "Average Annual Hours Worked" = `Annual avg. hours worked`) %>% 
  arrange(desc(`Average Annual Hours Worked`)) %>%

  mutate(bin_dist = paste(as.character(as.integer(`Happiness Level`)),as.character(as.integer(`Happiness Level`+1)), sep = "-")) %>%

  ggplot(aes(x = factor(bin_dist),
             y = `Average Annual Hours Worked`
             )) +
  geom_col()

@@

>>>>

Hours Worked vs. Happiness (factor in city)
Is there a correlation between happiness and hours worked?

```{r}
healthy_data_dot <- healthy_data_2 [-c(23),]

Healthy <- healthy_data_dot %>% 
  select(`City`, "Happiness Level" = `Happiness levels(Country)`, "Average Weekly Hours Worked" = `Hours Worked`) %>% 
  mutate(`Avg. Weekly Hours Worked` = factor(`Average Weekly Hours Worked`)) %>%

  #mutate(bin_dist = paste(as.character(as.integer(`Happiness Level`)),as.character(as.integer(`Happiness Level`+1)), sep = "-")) %>%

 ggplot(aes(x = `Happiness Level`, 
             y = `Avg. Weekly Hours Worked`, 
             color = `City`)) +
  geom_point() +
  scale_y_discrete(breaks = c(26.6, 30.6, 33.2, 38.8, 42.1))+

  labs(title = "Is there a correlation between weekly work hours and happiness levels?",
       x = "Happiness Level",
       y = "",
       caption = "Graph By Cat Terres; data sourced from Kaggle, 
       'Healthy Lifestyle Cities Report 2021'",
       color = "") +

  theme_foundation() +
  theme(legend.title=element_blank())+
  theme(legend.background = element_blank())

@@

```{r}
ggplotly(Healthy,
         tooltip = c("text",
                     "y",
                     "x",
                     "City"))
```
